A Shared Subspace Model for Multi-Group Covariance Estimation

### 2016-07-12 paper/arxiv/mscov.tex
Final pre-arxiv edits

\documentclass[12pt]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{textcomp}
\usepackage{longtable}
\usepackage{multirow, booktabs}
\usepackage{natbib}
\usepackage{url}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{chemarrow}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{tikz}
\usepackage[margin=.75in]{geometry}

@@

\title{Shared Subspace Models for Multi-Group Covariance Estimation
%
  \protect\thanks{Alexander M. Franks is a Moore/Sloan Data Science
    and WRF Innovation in Data Science Postdoctoral Fellow
    (\href{mailto:amfranks@uw.edu}{amfranks@uw.edu}).  Peter D. Hoff
    is a Professor at the Departments of Statistics and Biostatistics
    at the University of Washington
    (\href{mailto:pdhoff@uw.edu}{pdfhoff@uw.edu}).
%
This work was partially supported 
 by the Washington Research Foundation Fund for Innovation in
 Data-Intensive Discovery, the Moore/Sloan Data Science Environments
 Project at the University of Washington and NSF grant DMS-1505136.
%
 The authors are grateful to Dr.\ Daniel Promislow (Department of
 Pathology, University of Washington), Dr.\ Jessica Hoffman
 (University of Alabama at Birmingham) and Dr. Julie Jossie (INRIA)
 for sharing data and ideas which contributed to framing of this
 paper.}}  \author{Alexander Franks and Peter Hoff} \date{\today}
\maketitle 
\begin{abstract}

@@

  We develop a model-based method for evaluating heterogeneity among
  several $p\times p$ covariance matrices in the big $p$, small $n$ setting.
  This is done by assuming a spiked covariance model for each group
  and sharing information about the space spanned by the group-level
  eigenvectors.  We use an empirical Bayes method to identify a low-dimensional
  subspace which explains variation across all groups and use an MCMC
  algorithm to estimate the posterior uncertainty of eigenvectors and
  eigenvalues on this subspace.  The implementation and utility of our
  model is illustrated with analyses of high-dimensional multivariate
  gene expression and metabolomics data.
\\
\\
\noindent\textbf{Keywords:} covariance estimation; spiked covariance
model; Stiefel manifold; Grassmann manifold; big $p$, small $n$;
high-dimensional data; empirical Bayes.
\vfill
\end{abstract}

>>>>

\documentclass[12pt]{article}
\pdfoutput=1
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{textcomp}
\usepackage{longtable}
\usepackage{multirow, booktabs}
\usepackage{natbib}
\usepackage{url}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{chemarrow}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{tikz}
\usepackage[margin=.75in]{geometry}

@@

\title{Shared Subspace Models for Multi-Group Covariance Estimation
%
  \protect\thanks{Alexander M. Franks is a Moore/Sloan Data Science
    and WRF Innovation in Data Science Postdoctoral Fellow
    (\href{mailto:amfranks@uw.edu}{amfranks@uw.edu}).  Peter D. Hoff
    is a Professor in the Departments of Statistics and Biostatistics
    at the University of Washington
    (\href{mailto:pdhoff@uw.edu}{pdfhoff@uw.edu}).
%
This work was partially supported 
 by the Washington Research Foundation Fund for Innovation in
 Data-Intensive Discovery, the Moore/Sloan Data Science Environments
 Project at the University of Washington and NSF grant DMS-1505136.
%
 The authors are grateful to Dr.\ Daniel Promislow (Department of
 Pathology, University of Washington), Dr.\ Jessica Hoffman
 (University of Alabama at Birmingham) and Dr. Julie Josse (INRIA)
 for sharing data and ideas which contributed to framing of this
 paper.}}  \author{Alexander Franks and Peter Hoff} \date{\today}
\maketitle 
\begin{abstract}

@@

  We develop a model-based method for evaluating heterogeneity among
  several $p\times p$ covariance matrices in the large $p$, small $n$ setting.
  This is done by assuming a spiked covariance model for each group
  and sharing information about the space spanned by the group-level
  eigenvectors.  We use an empirical Bayes method to identify a low-dimensional
  subspace which explains variation across all groups and use an MCMC
  algorithm to estimate the posterior uncertainty of eigenvectors and
  eigenvalues on this subspace.  The implementation and utility of our
  model is illustrated with analyses of high-dimensional multivariate
  gene expression and metabolomics data.
\\
\\
\noindent\textbf{Keywords:} covariance estimation; spiked covariance
model; Stiefel manifold; Grassmann manifold; large $p$, small $n$;
high-dimensional data; empirical Bayes.
\vfill
\end{abstract}
